Hydras \& Co.

### 2022-01-10 doc/gaia-chapter.tex
experiments in bridge building

@@

>>>>

\section{Well formed ordinals}
For sake of compatibility, we add a clone of \texttt{hydra-battles}' type \texttt{E0} defined in \href{../theories/html/hydras.Epsilon0.E0.html}{Epsilon0.E0}.

\inputsnippets{T1Bridge/gE0Def}
\inputsnippets{T1Bridge/E0EqP}

In order to import definitions and lemmas
from~\href{../theories/html/hydras.Epsilon0.E0.html}{Epsilon0.E0}, we define a pair of translations.

\inputsnippets{T1Bridge/E0iotaPi}

These tools allow us to import \texttt{E0.lt}'s  well-foundedness.

\inputsnippets{T1Bridge/gE0LtWf}

@@

\begin{remark}
  The following snippets have been generated, not from
  \href{https://github.com/coq-community/gaia/blob/master/theories/ssete9.v}{gaia.ssete9.v}, but on a provisional copy:
\url{../theories/gaia/nfgaia.v} we made in order to insert comments for \alectr.  This copy is planned to be removed when we are able to add \alectr directives to a \coq source we are not allowed to modify.
\end{remark}
